Fast and Scalable Mixed Precision Euclidean Distance Calculations Using GPU Tensor Cores

### 2025-07-27 Paper/main.tex
Removed tcolorbox. Replace with titled-frame from framed.
tcolorbox is not an approved package. Was able to replicate it with a
titled-frame.

\usepackage[most]{tcolorbox}
\definecolor{mGreen}{rgb}{0,0.6,0}
\definecolor{mGray}{rgb}{0.5,0.5,0.5}
\definecolor{mPurple}{rgb}{0.58,0,0.82}
\definecolor{backgroundColour}{rgb}{0.95,0.95,0.92}

@@

\begin{tcolorbox}[colback=blue!5!white,colframe=blue!75!black,title=Box \#1: Selecting Tile Sizes Based on Data Reuse, label=box:tilesizeestimates, fontupper=\normalsize]

@@

{\bf (2)} Shared memory bandwidth is 17.9 TB/s. Therefore each value read from shared memory must be reused:
\[
\frac{\text{312}\times 10^{12}~\text{elements}}{\text{second}} \times \frac{\text{2 B}}{\text{1 element}} \times \frac{\text{second}}{\text{17.9 TB}} = \textbf{35 times}.
\]
   % \textbf{Conditions (1) \& (2) must be satisfied to realize peak performance.}
\end{tcolorbox}

@@

\subsubsection{Single Warp Tile}
\label{opt:warptile}
We create a $64{\times }64{\times }16$ warp tile (Figure \ref{fig:warp_mma}) that reuses each \prf\ and \qrf\ fragment, $4$ and $8$ times respectively, to achieve the required reuse calculated in Box~1. To reduce register pressure, only a single \sixtd \kslice is stored in registers at a time.

>>>>

\usepackage{framed}

\definecolor{TFFrameColor}{rgb}{0.0,0.0,0.5} % darkish blue frame
\definecolor{TFBackgroundColor}{rgb}{0.9,0.95,1} % light blue background
\definecolor{TFTitleColor}{rgb}{1,1,1} % white text

@@

\begin{titled-frame}{Box \#1: Selecting Tile Sizes Based on Data Reuse}

@@

{\bf (2)} Shared memory bandwidth is 17.9 TB/s. Therefore each value read from shared memory must be reused:
\[
\frac{\text{312}\times 10^{12}~\text{elements}}{\text{second}} \times \frac{\text{2 B}}{\text{1 element}} \times \frac{\text{second}}{\text{17.9 TB}} = \textbf{35 times}.
\]
   % \textbf{Conditions (1) \& (2) must be satisfied to realize peak performance.}
\end{titled-frame}

@@

\subsubsection{Single Warp Tile}
\label{opt:warptile}
We create a $64{\times }64{\times }16$ warp tile (Figure \ref{fig:warp_mma}) that reuses each \prf\ and \qrf\ fragment, $4$ and $8$ times respectively, to achieve the required reuse calculated in Box~\#1. To reduce register pressure, only a single \sixtd \kslice is stored in registers at a time.
